Of judges, aliens and total preorders

### 2021-02-01 paper/1901_3230880_philip_heltweg.tex
fix: more feedback by advisor

\section{Formal background}
\label{section:formal-background}

% TODO: put text here

\subsection{Propositional Logic} % Aussagenlogik
The following notation will be used, as proposed by \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables. Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively. $\models$ denotes classical logical consequence, $\equiv$ classical logical equivalence. $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.

@@

\section{Additional metadata for tpo revision}
% TODO: Text, put in that paper by booth and meyer starts here basically
\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$, Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of their paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. These functions are referred to as revision operators for $\leq$.

>>>>

\section{Formal background}
\label{section:formal-background}
The following notation will be used, largely aligned to Booth and Meyer \cite{Booth2011}: A propositional language $L$ generated from finitely many propositional variables. Lower case greek letters represent formulae in $L$ and $\top$, $\bot$ representing tautology and contradiction respectively. $\models$ denotes classical logical consequence, $\equiv$ classical logical equivalence. $Cn$ is used to denote the deductive closure of a formula or set of formulae in $L$.

@@

\section{Additional metadata for tpo revision}
After discussing notation and previous research, the following chapters present an excerpt of the new work done by Booth and Meyer in \cite{Booth2011}. To support their approach to tpo revision, Booth and Meyer propose adding additional metadata to epistemic states.

\subsection{Enriching epistemic states}
Based on DP-AGM and the postulates $(CR1)$-$(CR4)$, Booth and Meyer assume a fixed tpo $\leq$ over a set of worlds $W$ that acts as a plausibility ordering. The goal of their paper is the discussion of functions $\ast$ that return a new ordering $\leq_{\alpha}^{\ast}$ for every $\alpha \in L$. These functions are referred to as revision operators for $\leq$.
